Simulations of Ballot Polling Risk-Limiting Audits

### 2022-07-20 providence/sections/prov.tex
nicer plots
notes

>>>>

We now introduce the stopping condition of \Providence.
(TODO: add some more motivation and description of Providence... where minerva insists on a bound on the average risk providence only bounds the current path of the audit... it is nice because it sort of combines the main ratios of bravo and minerva)
